Duration Analysis for Performing-Dynamics performances

### 2021-01-11 material/expstimuli/analysis/expression/stim_d/duration.Rmd
organised files and updated readme
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Duration Analysis for Performing-Articulation performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

```{r extract, include = FALSE}
# onset
dt_onset <- fread("../filtered/data_correct_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv
dt_error_on <- fread("../filtered/data_error_correction_onset.csv", header = T, sep = ",", dec = ".") # read an error csv
# assign RowNr
dt_onset$RowNr <- rep(1:72, nrow(dt_onset)/72)
# sort by SubNr, BlockNr, TrialNr and NoteNr
dt_onset <- dt_onset[order(SubNr, BlockNr, TrialNr, RowNr),]
# include only articulation
dt_onset <- dt_onset[Condition == "performing" & Skill == "articulation"]

@@

# offset
dt_offset <- fread("../filtered/data_correct_offset.csv", header = T, sep = ",", dec = ".") # read a filtered csv
dt_error_off <- fread("../filtered/data_error_correction_offset.csv", header = T, sep = ",", dec = ".") # read an error csv
# assign RowNr
dt_offset$RowNr <- rep(1:72, nrow(dt_offset)/72)
# sort by SubNr, BlockNr, TrialNr and NoteNr
dt_offset <- dt_offset[order(SubNr, BlockNr, TrialNr, RowNr),]
# include only articulation
dt_offset <- dt_offset[Condition == "performing" & Skill == "articulation"]

@@

# assign subcomponents
dt_duration$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato2)){
  for (note in 1:length(ls_legato2[[phrase]])){
    dt_duration[RowNr == ls_legato2[[phrase]][note]]$Subcomponent <- "Legato"
  }
}
# Staccato
for (phrase in 1:length(ls_staccato2)){
  for (note in 1:length(ls_staccato2[[phrase]])){
    dt_duration[RowNr == ls_staccato2[[phrase]][note]]$Subcomponent <- "Staccato"
  }
}
```

@@

```{r duration, echo = FALSE}
# for each individual
duration <- dt_duration[Subcomponent == "Legato" | Subcomponent == "Staccato", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr, Subcomponent)]
print(duration)
```

@@

```{r duration_bar,  echo = FALSE}
p_duration <- ggplot(data = duration, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Normalised Duration", subtitle = "Duration: Performing-Articulation")
p_duration
```

@@

p_duration_seq <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Performing-Articulation(All)") +
  scale_x_continuous(breaks=seq(1,66,1)) + scale_y_continuous(breaks=seq(0,2,0.5), limits = c(0, 2))
p_duration_seq
```

#### Legato
```{r duration_seq_leg, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq_leg <- dt_duration[Subcomponent == "Legato", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

p_duration_seq_leg <- ggplot(data = duration_seq_leg, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Performing-Articulation(Legato)") +
  scale_x_continuous(breaks=seq(1,66,1))
p_duration_seq_leg
```

#### Staccato
```{r duration_seq_sta, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[Subcomponent == "Staccato", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

p_duration_seq_sta <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Performing-Articulation(Staccato)") +
  scale_x_continuous(breaks=seq(1,66,1))
p_duration_seq_sta
```

@@

#### Legato
```{r duration_dis_leg, fig.width = 12, echo = FALSE}
p_duration_dis_leg <- ggplot(dt_duration[Subcomponent == "Legato"], aes(x = normDu)) +
  geom_histogram(binwidth = .1, alpha=.5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Performing-Articulation(Legato)")
p_duration_dis_leg
```

#### Staccato
```{r duration_dis_sta, fig.width = 12, echo = FALSE}
p_duration_dis_sta <- ggplot(dt_duration[Subcomponent == "Staccato"], aes(x = normDu)) +
  geom_histogram(binwidth = .1, alpha = .5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Performing-Articulation(Staccato)")
p_duration_dis_sta
```

@@

### Valid performances (exclude outliers)
#### Legato
```{r outlier_leg, echo = FALSE}
# for legato
excluded_duration_leg <- duration[Subcomponent == "Legato" & Mean < duration_all[Subcomponent == "Legato"]$Mean+3*duration_all[Subcomponent == "Legato"]$SD & Mean > duration_all[Subcomponent == "Legato"]$Mean-3*duration_all$SD]
print(excluded_duration_leg)
```
- The number of excluded performance: `r duration_all[Subcomponent == "Legato"]$N-nrow(excluded_duration_leg)`

#### Staccato
```{r outlier_sta, echo = FALSE}
# for staccato
excluded_duration_sta <- duration[Subcomponent == "Staccato" & Mean < duration_all[Subcomponent == "Staccato"]$Mean+3*duration_all[Subcomponent == "Staccato"]$SD & Mean > duration_all$Mean-3*duration_all[Subcomponent == "Staccato"]$SD]
print(excluded_duration_sta)
```
- The number of excluded performance: `r duration_all[Subcomponent == "Staccato"]$N-nrow(excluded_duration_sta)`

```{r export, include = FALSE}
duration_valid <- dt_duration[, .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr)]
fwrite(duration_valid, "./duration_valid.csv")
```

>>>>

---
title: 'Duration Analysis for Performing-Dynamics performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

```{r extract, include = FALSE}
# onset
dt_onset <- fread("../filtered/data_correct_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv
dt_error_on <- fread("../filtered/data_error_correction_onset.csv", header = T, sep = ",", dec = ".") # read an error csv
# assign RowNr
dt_onset$RowNr <- rep(1:72, nrow(dt_onset)/72)
# sort by SubNr, BlockNr, TrialNr and NoteNr
dt_onset <- dt_onset[order(SubNr, BlockNr, TrialNr, RowNr),]
# include only dynamics
dt_onset <- dt_onset[Condition == "performing" & Skill == "dynamics"]

@@

# offset
dt_offset <- fread("../filtered/data_correct_offset.csv", header = T, sep = ",", dec = ".") # read a filtered csv
dt_error_off <- fread("../filtered/data_error_correction_offset.csv", header = T, sep = ",", dec = ".") # read an error csv
# assign RowNr
dt_offset$RowNr <- rep(1:72, nrow(dt_offset)/72)
# sort by SubNr, BlockNr, TrialNr and NoteNr
dt_offset <- dt_offset[order(SubNr, BlockNr, TrialNr, RowNr),]
# include only dynamics
dt_offset <- dt_offset[Condition == "performing" & Skill == "dynamics"]

@@

# assign subcomponents
dt_duration$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_forte2)){
  for (note in 1:length(ls_forte2[[phrase]])){
    dt_duration[RowNr == ls_forte2[[phrase]][note]]$Subcomponent <- "Forte"
  }
}
# Staccato
for (phrase in 1:length(ls_piano2)){
  for (note in 1:length(ls_piano2[[phrase]])){
    dt_duration[RowNr == ls_piano2[[phrase]][note]]$Subcomponent <- "Piano"
  }
}
```

@@

```{r duration, echo = FALSE}
# for each individual
duration <- dt_duration[Subcomponent == "Forte" | Subcomponent == "Piano", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr, Subcomponent)]
print(duration)
```

@@

```{r duration_bar,  echo = FALSE}
p_duration <- ggplot(data = duration, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Normalised Duration", subtitle = "Duration: Performing-Dynamics")
p_duration
```

@@

p_duration_seq <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Performing-Dynamics(All)") +
  scale_x_continuous(breaks=seq(1,66,1)) + scale_y_continuous(breaks=seq(0,2,0.5), limits = c(0, 2))
p_duration_seq
```

#### Forte
```{r duration_seq_leg, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq_leg <- dt_duration[Subcomponent == "Forte", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

p_duration_seq_leg <- ggplot(data = duration_seq_leg, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Performing-Dynamics(Forte)") +
  scale_x_continuous(breaks=seq(1,66,1))
p_duration_seq_leg
```

#### Piano
```{r duration_seq_sta, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_duration$TrialNr <- as.factor(dt_duration$TrialNr)
duration_seq <- dt_duration[Subcomponent == "Piano", .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr, RowNr)]

p_duration_seq_sta <- ggplot(data = duration_seq, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Normalised Duration", subtitle = "Duration: Performing-Dynamics(Piano)") +
  scale_x_continuous(breaks=seq(1,66,1))
p_duration_seq_sta
```

@@

#### Forte
```{r duration_dis_for, fig.width = 12, echo = FALSE}
p_duration_dis_for <- ggplot(dt_duration[Subcomponent == "Forte"], aes(x = normDu)) +
  geom_histogram(binwidth = .1, alpha=.5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Performing-Dynamics(Forte)")
p_duration_dis_for
```

#### Piano
```{r duration_dis_pia, fig.width = 12, echo = FALSE}
p_duration_dis_pia <- ggplot(dt_duration[Subcomponent == "Piano"], aes(x = normDu)) +
  geom_histogram(binwidth = .1, alpha = .5, position="identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised Duration", y = "Count", subtitle = "Duration: Performing-Dynamics(Piano)")
p_duration_dis_pia
```

@@

### Valid performances (exclude outliers)
#### Forte
```{r outlier_leg, echo = FALSE}
# for forte
excluded_duration_for <- duration[Subcomponent == "Forte" & Mean < duration_all[Subcomponent == "Forte"]$Mean+3*duration_all[Subcomponent == "Forte"]$SD & Mean > duration_all[Subcomponent == "Forte"]$Mean-3*duration_all$SD]
print(excluded_duration_for)
```
- The number of excluded performance: `r duration_all[Subcomponent == "Forte"]$N-nrow(excluded_duration_for)`

#### Piano
```{r outlier_sta, echo = FALSE}
# for piano
excluded_duration_pia <- duration[Subcomponent == "Piano" & Mean < duration_all[Subcomponent == "Piano"]$Mean+3*duration_all[Subcomponent == "Piano"]$SD & Mean > duration_all$Mean-3*duration_all[Subcomponent == "Piano"]$SD]
print(excluded_duration_pia)
```
- The number of excluded performance: `r duration_all[Subcomponent == "Piano"]$N-nrow(excluded_duration_pia)`

<!-- ```{r export, include = FALSE} -->
<!-- duration_valid <- dt_duration[, .(N = length(normDu), Mean = mean(normDu)), .(SubNr, TrialNr)] -->
<!-- fwrite(duration_valid, "./duration_valid.csv") -->
<!-- ``` -->
